---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkd

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/paleolimbot/pkd/workflows/R-CMD-check/badge.svg)](https://github.com/paleolimbot/pkd/actions)
[![Codecov test coverage](https://codecov.io/gh/paleolimbot/pkd/branch/master/graph/badge.svg)](https://codecov.io/gh/paleolimbot/pkd?branch=master)
<!-- badges: end -->

The goal of pkd is to provide cross-platform integer and floating-point vector types commonly used to read and write files.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("paleolimbot/pkd")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(pkd)

# logical
lgl1(0xff)
lgl8(0x01)

# integer
int8(0xff)
uint8(0xff)
int16(c(0xff, 0xff))
uint16(c(0xff, 0xff))
int32(c(0xff, 0xff, 0xff, 0xff))
uint32(c(0xff, 0xff, 0xff, 0xff))
int64(c(0xff, 0xff, 0xff, 0xff, 0xff, 0xff, 0xff, 0xff))
uint64(c(0xff, 0xff, 0xff, 0xff, 0xff, 0xff, 0xff, 0xff))

# floating-point
as_dbl32(12.34)
as_dbl64(12.34)
```

Currently, `Math` and `Ops` are not implemented; however, coercion to `integer()`/`double()`, subsetting, endian-swapping, and subset-assignment are supported:

```{r}
x <- as_uint8(1:10)
x
x[1:5]

x[5] <- 255
x

uint32(c(0x00, 0x00, 0x00, 0x01), endian = 1L)
uint32(c(0x00, 0x00, 0x00, 0x01), endian = 0L)

pkd_ensure_endian(
  uint32(c(0x00, 0x00, 0x00, 0x01), endian = 0L), 
  endian = 1L
)
```

Under the hood, these vectors are implemented as `raw()` vectors as part of an S3 object. This design allows a great deal of code to be recycled among the various fixed-width types.

```{r}
unclass(as_uint32(255))
```
